---
title: "colouR"
author: "Alan Inglis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{colouR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction to the colouR Package

Welcome to the `colouR` package, a useful tool for analyzing and utilizing the colors in images, as well as providing color palettes inspired by Radiohead and Taylor Swift album covers. Whether you are a designer looking for inspiration, a data analyst searching for unique ways to visualize data, or a music lover wanting to incorporate your favorite album colors into your projects, this package is for you.

# Package Overview

The `colouR` package provides a set of functions that allows you to:

* Extract color values from an image (either JPG or PNG).
* Obtain the top n colors in the image based on their frequency.
* Exclude black and white shades, if desired.
* Group and average colors in the image.
* Utilize color palettes inspired by Radiohead and Taylor Swift album covers.
* These functionalities make the `colouR` package a versatile and easy-to-use tool for exploring and working with colors in images.

# Key Functions

Some of the main functions included in the `colouR` package are:

* `getTopCol()`: Extracts the top n colors from an image, with options to exclude black and white shades, and to group and average colors.

* `colPalette()`: Creates a color palette based on a specified album cover from either Radiohead or Taylor Swift discography.

* `scaleColor()`: Provides a ggplot2-compatible color scale based on the selected album cover palette, for both discrete and continuous data.

* `scaleFill()`: Provides a ggplot2-compatible fill scale based on the selected album cover palette, for both discrete and continuous data.

# Getting Started

To begin using the `colouR` package, simply install it from CRAN or GitHub, load it into your R session, and start exploring the world of colors in images and your favorite music album covers.

```{r}
# Install the package (if not already installed)
#install.packages("colorXtractor")

# Load the package
library(colouR)

# Extract top colors from an image
getTopCol("/Users/alaninglis/Desktop/taylor/tyty.png", n = 5)
```


TEST 2

```{r}
# Create a color palette based on a Taylor Swift album cover
tswift_palette <- colPalette(palette = "evermore")
tswift_palette(12)
```


TEST 3

```{r}
library(ggplot2)
# Apply a Radiohead color scale to a ggplot2 plot
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scaleFill(palette = "KID_A", guide = "none")
```


THE END
